### 2022-11-28 dissertation/chapters/07-methodology.tex
🗃️ (data): Removing old data

So far, this dissertation has provided background information on \acfp{ANN}, \index{heuristic}heuristics, \acf{HH} and probability theory in Chapters \ref{chap:anns}-\ref{chap:probability}. Chapter \ref{chap:bhh} provided the detail of the implementation of the proposed \acs{BHH} with all its components and hyper-parameters. Scientific experimentation can now be conducted. Chapter \ref{chap:introduction} identified a set of empirical goals for this dissertation. The goals of this dissertation include an empirical evaluation of the \acs{BHH}, its behaviour and performance, and a comparison to state of the art low-level \index{heuristic}heuristics. This chapter provides the detailed specification of the methodology that is followed for the empirical process. Details are provided on the implementation of experiments, datasets, selection of hyper-parameters and design decisions. The process by which the results are statistically analysed are also presented. The remainder of the chapter is structured as follows:

>>>>

So far, this dissertation has provided background information on \acfp{ANN}, \index{heuristic}heuristics, \acp{HH} and probability theory in Chapters \ref{chap:anns} to \ref{chap:probability}. Chapter \ref{chap:bhh} provided the detail of the implementation of the proposed \acs{BHH} with all its components and hyper-parameters. Scientific experimentation can now be conducted. Chapter \ref{chap:introduction} identified a set of empirical goals for this dissertation. The goals of this dissertation include an empirical evaluation of the \acs{BHH}, its behaviour and performance, and a comparison to state of the art low-level \index{heuristic}heuristics. This chapter provides the detailed specification of the methodology that is followed for the empirical process. Details are provided on the implementation of experiments, datasets, selection of hyper-parameters and design decisions. The process by which the results are statistically analysed are also presented. The remainder of the chapter is structured as follows:
